A Comparison of Different GANs for Generating Handwritten Digits on MNIST

### 2020-04-11 proposal.tex
Outlined rest of paper and started conclusion.

\section{\label{sec:level1}Background}

@@

\subsection{\label{sec:level2}Applications}

@@

\subsection{\label{sec:level2}Wasserstein Generative Adversarial Networks}

@@

\subsection{\label{sec:level2}Research Questions}

@@

>>>>

\section{\label{sec:background}Background}

@@

\subsection{\label{sec:applications}Applications}

@@

\subsection{\label{sec:wgan}Wasserstein Generative Adversarial Networks}

@@

\subsection{\label{sec:researchQuestions}Research Questions}

@@

% ------------------------------------------------ Implementation -----
\section{\label{sec:implementation}Implementation}
% go over how each algorithm was implemented,
% possibly link to github with code

\subsection{\label{sec:impVanilla}Vanilla Generative Adversarial Network}
% section covering basic GAN implementation

\subsection{\label{sec:impDCGAN}Deep Generative Adversarial Network}
% section covering code used to run DCGAN

\subsection{\label{sec:impWGAN}Wasserstein Generative Adversarial Network}
% section covering WGAN code

%---------------------------------------------- end implementation

%---------------------------------------------- experiment --------------
\section{\label{sec:exp}Experiments}
% goes over the tests ran in the experiment

This section goes over in depth the experiments ran in this project and the results produced from them.

\subsection{\label{sec:dataSet}Data Set}
% describe the mnist data set

\subsection{\label{sec:expQuality}Quality}
% simple test where we show our best outputs from each gan

\subsection{\label{sec:expTime}Time for Training}
% time for each generation? Sorta wishy washy on this one

\subsection{\label{sec:expData}Quantity of Training Data}
% vary the amount of training data available to the gans

%---------------------------------------- end experiment ----------------

\section{\label{sec:exp}Conclusions}
% high level conclusion of results and future work

This project paves a useful survey and comparison of three popular GAN architectures. Based on the results we can conclude that....

Future work for this project would entail researching more GAN architectures like Conditional GANS (CGANS), Least Square GANs (LSGAN), Auxiliary Classifier GAN (ACGAN), and Info GANS (infoGAN) \cite{cGAN, lsgan, acgan, infogan},. Another avenue of research would be to examine how the results of our experiments on the MNIST dataset hold up against different data-sets.

Since this is such a new algorithm in the field of Artificial intelligence, people are still actively doing a ton of research in GANs pushing them at the forefront of cutting edge. As GANs become more widely used in the public and private sector, we are sure to see a lot more research into the applications of GANs.

\section{Acknowledgment}

This project was submitted as a RIT CSCI-431 project for professor Sorkunlu's class.
